### 2014-04-18 tex/discussion_notes.tex
paper update

@@

\subsection{False Negative Analysis}

@@

@@

Let $\mathcal{C}^1$ denote the set of univariate convex functions supported on $[-b,b]$. Let $\mathcal{C}^1_L \equiv \{ f \in \mathcal{C}^1 \,:\, \| \partial f \|_\infty \leq L \}$ denote the set of $L$-Lipschitz univariate convex functions. \\

Define $\mathcal{C}^s$ as the set of convex additive functions
\[
\mathcal{C}^s \equiv \{ f \,:\, f = \sum_{k=1}^s f_k, \,
   f_k \in \mathcal{C}^1 \}
\]
We will also define classes of bounded and Lipschitz convex additive functions. 
\begin{align*}
\mathcal{C}^s_B &= \{ f \in \mathcal{C}^s \,:\, 
  \| f \|_\infty \leq B \} \\
\mathcal{C}^s_L &= \{ f \in \mathcal{C}^s \,:\, 
f = \sum_{k=1}^s f_k, \, \| \partial f_k \|_\infty \leq L \}
\end{align*}

Let $f^*(x) = \sum_{k=1}^s f^*_k(x_k)$ be the population risk minimizer:
\[
f^* = \arg\min_{f \in \mathcal{C}^s} \E \Big( f_0(X) - f^*(X) \Big)^2
\]

We let $B$ be an upper bound on $\|f_0\|_\infty$ and $\| f^* \|_\infty$ and let $L$ be an upper bound on $\| \partial_{x_k} f_0 \|_\infty$ and $\| \partial f^*_k \|_\infty$.

In the finite sample context where we have $n$ samples $x_1, ..., x_n$, we will abuse notation and let $y, f_0, f^*, w$ denote their de-meaned counterpart, that is, $f_0$ is an $n$-dimensional vector whose coordinate $i$ is $f_0(x_i) - \frac{1}{n} \sum_i f_0(x_i)$.

We define $\hat{f}$ as the empirical risk minimizer:
\[
\hat{f} = \arg\min \{ \| y - f \|_n^2 + \lambda \sum_{k=1}^s \| f_k \|_\infty 
    \,:\, f \in \mathcal{C}^s_L, \mathbf{1}_n^\tran f_k = 0 \}
\]

We also define $\hat{f}^*$ as the noiseless empirical risk minimizer:
\[
\hat{f}^* = \arg\min \{ \| f_0 - f \|_n^2 \,:\, 
f \in \mathcal{C}^s_L, \mathbf{1}_n^\tran f_k = 0\}
\]

We start from the definition.

@@

\section{2/15/2014}

>>>>

\mathchardef\mh="2D

@@

$Y'_i = Y_i - \hat{f}(X_i) = f_0(X_i) + w_i - \hat{f}(X_i)$. Both $f_0(X_i)$ and $\hat{f}(X_i)$ are bounded by $2 sLb$.

For a single $w_i$, we know that with probability at least $1-\delta$, $|w_i| \leq \mathbf{c} \sigma \sqrt{ \log \frac{2}{\delta} }$. Therefore, taking an union bound and setting $\delta = 1/n$, we have that $\max_i |w_i| \leq \mathbf{c} \sigma \sqrt{\log n} $ with probability at least $1 - \frac{1}{n}$.

Putting this together, $\| Y' \|_\infty \leq \mathbf{c}(sLb + \sigma\sqrt{\log n}) \leq
 \mathbf{c} sLb \sigma\sqrt{\log n}$.\\

Now, we also need to bound the mean of $Y'$:

\begin{align*}
&\frac{1}{n} \sum_{i=1}^n f_0(X_i) + w_i - \hat{f}(X_i) \\
=& \frac{1}{n} \sum_{i=1}^n f_0(X_i) + w_i 
\end{align*}
The first mean $\frac{1}{n} \sum_{i=1}^n f_0(X_i)$ is the average of $n$ bounded zero-mean random variables since $| f_0(X_i) | \leq 2 s L b$. Therefore, the first term is at most $ sLb \sqrt{\frac{1}{n} \log \frac{2}{\delta}$ with probability at least $1-\delta$.

The second mean is the average of $n$ subgaussian random variables with subgaussian scale $\sigma$. Therefore, the second term is at most $\sigma\sqrt{\frac{1}{n} \log \frac{2}{\delta}}$.

The mean of $Y'$ is therefore at most $\mathbf{c} (sLb + \sigma) \sqrt{ \frac{1}{n} \log n}$ with probability at least $1 - \frac{1}{n}$.

By Serfling and union bound, with probability at least $1-\frac{1}{n}$, we have that the deviation for all $i$
\begin{align*}
\Big| \frac{1}{n} \mathbf{1}_{i:n}^\tran Y' \Big| &\leq \mathbf{c} sLb\sigma \sqrt{\log n} 
\sqrt{\frac{1}{n} \log 2np} + \mathbf{c} (sLb + \sigma) \sqrt{\frac{1}{n} \log np}\\
  &\leq \mathbf{c} sLb \sigma \sqrt{\frac{1}{n} \log n \log np }
\end{align*}

Plugging this in and plugging in $\lambda > \mathbf{c} sLb \sigma \sqrt{
  \frac{1}{n} \log n \log np}$, we have that:

\begin{align*}
\frac{1}{n} \sum_{i' > j} \mathsf{gap}_{i'} \mathbf{1}_{i':n}^\tran Y' 
   + \lambda (X_{kn} - X_{kj})a &\geq 
 \lambda (X_{kn} - X_{kj}) a 
    - \sum_{i'>j}\mathsf{gap}_{i'} \mathbf{c} sLb\sigma \sqrt{\frac{1}{n} \log n \log np} \\
&\geq \lambda (X_{kn} - X_{kj}) a - (X_{kn} - X_{kj}) 
    \mathbf{c} s Lb \sigma \sqrt{\frac{1}{n} \log n \log np} \\
&\geq 0 
\end{align*}

\newpage
\subsection{False Negative Analysis}

@@

\subsubsection{Notation}

Where $f : \R^p \rightarrow \R$, we let $\| f \|_P \equiv \E f(X)^2 $.

@@

\begin{itemize}

\item Let $\mathcal{C}^1$ denote the set of univariate convex functions supported on $[-b,b]$. Let $\mathcal{C}^1_L \equiv \{ f \in \mathcal{C}^1 \,:\, \| \partial f \|_\infty \leq L \}$ denote the set of $L$-Lipschitz univariate convex functions. \\

\item Define $\mathcal{C}^s$ as the set of convex additive functions
\[
\mathcal{C}^s \equiv \{ f \,:\, f = \sum_{k=1}^s f_k, \,
   f_k \in \mathcal{C}^1 \}
\]
\item We will also define classes of bounded and Lipschitz convex additive functions. 
\begin{align*}
\mathcal{C}^s_B &= \{ f \in \mathcal{C}^s \,:\, 
  \| f \|_\infty \leq B \} \\
\mathcal{C}^s_L &= \{ f \in \mathcal{C}^s \,:\, 
f = \sum_{k=1}^s f_k, \, \| \partial f_k \|_\infty \leq L \}
\end{align*}

\item Let $f^*(x) = \sum_{k=1}^s f^*_k(x_k)$ be the population risk minimizer:
\[
f^* = \arg\min_{f \in \mathcal{C}^s} \| f_0 - f^* \|_P^2
\]

\item We let $B$ be an upper bound on $\|f_0\|_\infty$ and $\| f^* \|_\infty$ and let $L$ be an upper bound on $\| \partial_{x_k} f_0 \|_\infty$ and $\| \partial f^*_k \|_\infty$.

\item We define $\hat{f}$ as the empirical risk minimizer:
\[
\hat{f} = \arg\min \{ \| y - f \|_n^2 + \lambda \sum_{k=1}^s \| f_k \|_\infty 
    \,:\, f \in \mathcal{C}^s_L, \mathbf{1}_n^\tran f_k = 0 \}
\]

\item We also define $\hat{f}^*$ as the noiseless empirical risk minimizer:
\[
\hat{f}^* = \arg\min \{ \| f_0 - f \|_n^2 \,:\, 
f \in \mathcal{C}^s_L, \mathbf{1}_n^\tran f_k = 0\}
\]

\item For $k \in \{1,...,s\}$, define $g^*_k$ to be decoupled concave population risk minimizer
\[
g^*_k \equiv \min_{g_k \in \mh \mathcal{C}} \| f_0 - f^*_{-k} - g_k \|_P^2
\]
In our proof, we will analyze $g^*_k$ for $k$'s such that $f^*_k = 0$.

\item Also, we define the noiseless empirical version:
\[
\hat{g}^*_k \equiv \min_{g_k \in \mh \mathcal{C}_L} \| f_0 - f^*_{-k} - g_k \|_n^2
\]

\item Likewise, we define the empirical version
\[
\hat{g}_k \equiv \min_{g_k \in \mh \mathcal{C}_L} \| y - \hat{f} - g_k \|_n^2
\]
By the definition of the ACDC procedure, $\hat{g}_k$ exist only for $k$ that have zero in their convex additive approximation.

\newpage
\subsubsection{Proof outline}

The \textbf{final step} is to show the following:
\begin{align*}
\| f_0 - \hat{f} \|_P & \approx \| f_0 - f^* \|_P \\
\| f_0 - f^* - \hat{g}_k \|_P & \approx \| f_0 - f^* - g^*_k \|_P \quad \trm{for all $k \in \{1,...,s\}$ where $f^*_k = 0$}
\end{align*}
where the difference is a term that decreases with $n$.

Suppose $\hat{f}_k = 0$ and $f^*_k \neq k$, then for large enough $n$, there must be a contradiction because $\| f_0 - f^* \|_P > \| f_0 - f^{*(s-1)} \|_P$. We would have a contradiction.

Suppose $f^*_k = 0$, then $g^*_k \neq 0$. We would have another contradiction.

\rule{5cm}{0.4pt}
\vspace{0.2in}

Concavity, \textbf{removing} sample-dependent convex fucntions.\\

For arbitrary function $g$, we have the following:
\begin{align*}
\| f_0 - \hat{f} - g \|_n = \| f_0 - \hat{f} + f^* - f^* - g \|_n 
   & \leq \| f_0 - f^* -g \|_n
       + \| \hat{f} - f^* \|_n \\
   &\geq \| f_0 - f^* - g \|_n - \| \hat{f} - f^* \|_n 
\end{align*}

Therefore:
\begin{align*}
\| f_0 - f^* - g \|_n^2 - 2 \| f_0 - f^* - g\|_n \| \hat{f} - f^* \|_n \leq
  \| f_0 - \hat{f} - g \|_n^2 \leq
  \| f_0 - f^* -g \|_n^2 + 2 \| f_0 - f^* - g \|_n \| \hat{f} - f^* \|_n 
\end{align*}

The radius of approximation is $2 \| f_0 - f^* - g \|_n \| \hat{f} - f^* \|_n$, which we need to upper bound. $\| f_0 - f^* - g \|_n \leq \mathbf{c} sLb$.

\rule{5cm}{0.4pt}
\vspace{0.2in}

We \textbf{start} from the definition. We don't need to force $y$ to be zero-mean.

@@

The $\| f_0 - \hat{f} \|_n^2 - \| f_0 - \hat{f}^* \|_n^2$ term is always positive. We want to lower bound the second term with a negative quantity.

One way to proceed:
$\| \hat{f}^*_k \|_\infty \leq 2bL$. And because $\hat{f}^*$ minimizes

\textbf{Note:}
The $\hat{f}^*$ here could be any function that does depend on the noise. The advantage of having $\hat{f}^*$ is that $\| f_0 - \hat{f} \|_n^2 - \| f_0 - \hat{f}^* \|_n^2 \geq \| \hat{f} - \hat{f}^* \|_n^2$.

\rule{5cm}{0.4pt}
\vspace{0.2in}

\textbf{Continuation from start}.
Taking the \textbf{start} derivation and instead of comparing against $\hat{f}^*$, we will instead compare against $f^*$ (de-meaned).

Since the samples $X_1, ..., X_n$ are clear from context, we denote $\bar{f}^*$ as $\frac{1}{n} \sum_{i=1}^n f^*(X_i)$.

All parts still work and we get down to the following inequality:
\begin{align*}
\| f_0 - \hat{f} \|_n^2 - \|f_0 - f^* + \bar{f}^* \|_n^2 &\leq 
      2 | \langle w, \hat{f} - f^* + \bar{f}^* \rangle | + \lambda 2sLb \\
  &\leq \mathbf{c} (sLb)^2 \sigma \sqrt{ \frac{1}{n} \log 4n } + 
   \lambda 2 s L b
\end{align*}
with probability at least $1-\frac{1}{n}$.\\

We use the \emph{centering effect} analysis. Since with high probability ($1-\frac{1}{n}$) 
\[
\|f_0 - \hat{f}\|_n^2 - 
  \Big( \|f_0 - f^*\|_n^2 + \mathbf{c} (sLb)^2 \frac{1}{n} \log 4n \Big) \leq 
\|f_0 - \hat{f} \|_n^2 - \|f_0 - f^* + \bar{f}^*\|_n^2
\]
Therefore, with probability at least $1-\frac{2}{n}$,
\begin{align*}
\|f_0 - \hat{f}\|_n^2 - \|f_0 -f^*\|_n^2 &\leq \mathbf{c}(sLb)^2 \frac{1}{n} \log 4n
      + \mathbf{c} (sLb)^2 \sigma \sqrt{\frac{1}{n} \log 4n } + \lambda 2 sLb \\
 &\leq \mathbf{c} (Lb)^2\sigma \sqrt{\frac{s^4}{n} \log 4n} + \lambda 2 sLb
\end{align*}

Now, we use the the \emph{uniform convergence} result. With probability at least $1-\frac{3}{n}$

\begin{align*}
\| f_0 - \hat{f}\|_P^2 - \| f_0 - f^*\|_P^2 & \leq
   \mathbf{c} (Lb)^2 \sigma \sqrt{\frac{s^4}{n} \log 4n} + \lambda 2 s Lb +
   \mathbf{c} (Lb)^3 \sqrt{\frac{s^5}{n^{4/5}} \log 2n} \\
 &\leq \mathbf{c} (Lb)^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log 4n} + \lambda 2 s Lb
\end{align*}

\rule{5cm}{0.4pt}
\vspace{0.2in}

\textbf{f convergence}.

Here, our goal is to bound $\| \hat{f} - f^* \|_n^2$.

Since $f^* = \arg\min_{f \in \mathcal{C}^s} \| f_0 - f \|_P^2$, we have that
\begin{align*}
\|f^* - \hat{f} \|_P^2 &\leq \|f_0 - \hat{f} \|_P^2 - \| f_0 - f^* \|_P^2 \\
 &\leq \mathbf{c} (Lb)^3 \sqrt{ \frac{s^5}{n^{4/5}} \log 4n} + \lambda 2s Lb
\end{align*}

Now, by \emph{uniform convergence} again, we have:

\[
\| f^* - \hat{f} \|_n^2 \leq \mathbf{c} (Lb)^3 \sqrt{\frac{s^5}{n^{4/5}} \log 4n} + 
      \mathbf{c} \lambda s L b
\]

\rule{5cm}{0.4pt}
\vspace{0.2in}

\textbf{Centering Effect}

Here, we bound the difference of $\| f_0 - f^* + \bar{f}^* \|_n^2$ and $\| f_0 - f^* \|_n^2$.

\begin{align*}
\| f_0 - f^* + \bar{f}^* \|_n^2 &= \| f_0 - f^* \|_n^2 
    + 2 \langle f_0 - f^*, \bar{f}^* \rangle + \bar{f}^{*2} \\
  &= \| f_0 - f^* \|_n^2 + 2 \bar{f}^* \langle f_0 - f^*, \mathbf{1} \rangle_n + 
    \bar{f}^{*2} \\
  &= \| f_0 - f^* \|_n^2 + 2 \bar{f}^* \bar{f}_0 - \bar{f}^{*2}
\end{align*}

$\bar{f}^* = \frac{1}{n} \sum_{i=1}^n f^*(X_i)$ is the average of $n$ bounded mean-zero random variables and therefore, with probability at least $1-\delta$, $| \bar{f}^* | \leq 4 s L b \sqrt{ \frac{1}{n} \log \frac{2}{\delta} }$.

The same reasoning likewise applies to $\bar{f}_0 = \frac{1}{n} \sum_{i=1}^n f_0(X_i)$.

Taking a union bound and letting $\delta = \frac{1}{n}$, we have that, with probability at least $1- \frac{1}{n}$,

\begin{align*}
| \bar{f}^* | | \bar{f}_0 | &\leq \mathbf{c} (sLb)^2 \frac{1}{n} \log 4 n \\
\bar{f}^{*2} &\leq \mathbf{c} (sLb)^2 \frac{1}{n} \log 4 n
\end{align*}

Therefore, with probability $1-\frac{1}{n}$,
\[
\|f_0 - f^*\|_n^2 - \mathbf{c} (sLb)^2 \frac{1}{n} \log 4 n \leq
    \| f_0 - f^* + \bar{f}^* \|_n^2 \leq 
\|f_0 - f^*\|_n^2 + \mathbf{c} (sLb)^2 \frac{1}{n} \log 4 n
\]

\rule{5cm}{0.4pt}
\vspace{0.2in}

\textbf{Denoising}

Here we outline how to bound $\langle w, \hat{f} - \hat{f}^* \rangle$ where $\hat{f}^*$ can be any function that doesn't depend on $w$.

We suppose that both $\hat{f}, \hat{f}^*s \in \mathcal{C}^s_L$.

By Bronshtein, we know that:
\begin{align*}
\log N_\infty(\epsilon, \mathcal{C}_L^1) &= C bL \epsilon^{-1/2} \\
\log N_\infty(\epsilon, \mathcal{C}_L^s) &= C sbL s^{1/2} \epsilon^{-1/2} 
\end{align*}

Clearly, the covering number would not change if we center the set $\mathcal{C}_L^s$ around $\hat{f}^*$, call this $\mathcal{G}$. The difference $\hat{f} - \hat{f}^* \in \mathcal{G}$

For all $h \in \mathcal{G}$:
\begin{align*}
|\langle w, h \rangle_n | &= |\langle w, h - h_\epsilon \rangle_n | 
     + |\langle w, h_\epsilon \rangle_n | \\
 &\leq \frac{1}{n} \| w \|_1  \epsilon + |\langle w, h_\epsilon \rangle_n \| 
\end{align*}

Therefore
\[
\sup_{g \in \mathcal{G}} | \langle w, h \rangle_n | \leq 
      \frac{1}{n} \|w\|_1 \epsilon + 
      \sup_{h_\epsilon \in \mathcal{G}_\epsilon} | \langle w, h_\epsilon \rangle_n |
\]

The final goal is to show that $\sup_{h \in \mathcal{G}} | \langle w, h \rangle_n | \leq 
\textrm{constants} \cdot \sqrt{\frac{1}{n^{4/5}}}$.

\rule{5cm}{0.4pt}
\vspace{0.2in}

\textbf{Chaining}.

Our goal is to give a precise bound for $\sup_{h \in \mathcal{G}} | \langle w, h \rangle|$.

We first restate the chaining theorem. Suppose $\| g \|_n \leq R$ for all $g \in \mathcal{G}$.

Suppose $\epsilon > \frac{1}{\sqrt{n}}\sigma \mathbf{c} \int_0^R \sqrt{ \log N_2(t, \mathcal{G}) }dt \vee R $. 
Then we have that
\[
P\Big( \sup_{g \in \mathcal{G}} \langle w, g \rangle_n \geq \epsilon \Big) \leq
  4 \exp \Big( - \frac{ n \epsilon^2}{ \mathbf{c} R^2 \sigma^2} \Big)
\]
In our case, $R \leq sLb$.

Restated, we have that, with probablity at least $1-\delta$,
\[
\sup_{g \in \mathcal{G}} | \langle w, g \rangle_n | \leq 
   \mathbf{c} sLb \sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta}} + 
      \Big( \int_0^R \sqrt{\log N_2(t, \mathcal{G})}dt \vee R \Big)\, 
       \mathbf{c} \sigma \sqrt{\frac{1}{n}} 
\]

Now we evaluate the integral. Since $N_2(t, \mathcal{G}) \leq N_\infty(t, \mathcal{G})$, we know that $\sqrt{\log N_2(t, \mathcal{G})} \leq \sqrt{C s^{1.5} b L} t^{-1/4}$.

\begin{align*}
\int_0^R \sqrt{\log N_2(t, \mathcal{G})} dt &\leq 
      \sqrt{C s^{1.5} b L} \int_0^R t^{-1/4} dt \\ 
 &= \sqrt{C s^{1.5} b L} \, \frac{4}{3} R^{3/4} \\
 &= \sqrt{C s^{1.5} b L} \, \mathbf{c} (sLb)^{3/4} \\
 &\leq \mathbf{c} (s b L)^2
\end{align*}

Coming back, we have, with probability at least $1-\delta$,
\begin{align*}
\sup_{g \in \mathcal{G}} | \langle w, g \rangle | &\leq 
    \mathbf{c} sLb \sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta} } + 
    \mathbf{c} (sLb)^2 \sigma \sqrt{ \frac{1}{n} } \\
 &\leq \mathbf{c} (sLb)^2\sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta} }
\end{align*}

\rule{5cm}{0.4pt}
\vspace{0.2in}

\textbf{Uniform convergence}:

The goal is to bound 
$\sup_{f \in \mathcal{C}^s_L} \Big| \| f_0 - f \|^2_n - \|f_0 - f \|^2_P\Big|$. \\

Again, let $\mathcal{G}$ denote the off-centered set of convex functions, that is, $\mathcal{G} \equiv \mathcal{C}^s_L - f_0$.

First, note that if $h \in \mathcal{G}$, then $\| h \|_\infty = \| f_0 - f \|_\infty \leq 4 s b L$.

Because $\| h \|_n = \| h - h_\epsilon + h_\epsilon \|_n$, we have that
\begin{align*}
\|h_\epsilon \|_n - \| h - h_\epsilon \|_n &\leq 
    \| h \|_n \leq \|h_\epsilon \|_n + \| h - h_\epsilon \|_n \\
\|h_\epsilon \|_n - \epsilon &\leq 
    \| h \|_n \leq \|h_\epsilon \|_n + \epsilon  \\
\| h_\epsilon \|^2_n - 8 \epsilon (s L b)  &\leq \| h  \|^2_n  \leq
   \| h_\epsilon \|_n^2 + 8 \epsilon (s L b) 
\end{align*}
where we used the fact that $\| h - h_\epsilon \|_n \leq \| h - h_\epsilon \|_\infty \leq \epsilon$ and $ \| h_\epsilon \|_n \leq \| h_\epsilon \|_\infty \leq 4 s L b$.

And likewise:
\begin{align*}
\| h_\epsilon \|^2_P - 8 \epsilon (s L b)  &\leq \| h  \|^2_P \leq
   \| h_\epsilon \|_P^2 + 8 \epsilon (s L b)
\end{align*}

Therefore, 
\begin{align*}
\sup_{h \in \mathcal{G}}  \Big| \|h\|^2_n - \|h\|^2_P \Big| \leq 
\sup_{h_\epsilon} \Big| \|h_\epsilon\|^2_n - \|h_\epsilon\|^2_P \Big| 
        + \epsilon (16 sLb)
\end{align*}

Since $\| h_\epsilon \|_n^2 = \frac{1}{n} \sum_{i=1}^n h_\epsilon(X_i)^2$ is an average of bounded random variables, we have by Union Bound and Hoeffding Inequality that, with probability at most $1 - \delta$,
\begin{align*}
\sup_{h_\epsilon} \Big| \|h_\epsilon\|^2_n - \|h_\epsilon\|^2_P \Big| &\leq
  (8sLb)^2 \sqrt{ \frac{1}{cn} \big(\log \frac{2}{\delta} 
        + \log N_\infty(\epsilon, \mathcal{C}_L^s) \big) } \\
&\leq (8sLb)^2 \sqrt{ \frac{1}{cn} \big(\log \frac{2}{\delta} 
        + C s^{1.5} Lb \epsilon^{-1/2}   \big) }
\end{align*}

We will set $\epsilon = \frac{1}{n^{2/5}} (C s^{0.5} L b)^2$ and $\delta = \frac{1}{n}$. 
Therefore:
\begin{align*}
\sup_{h_\epsilon} \Big|  \|h_\epsilon\|^2_n - \|h_\epsilon\|^2_P \Big| &\leq
   (8sLb)^2 \sqrt{ \frac{1}{cn} \big(\log \frac{2}{\delta} 
        + s n^{1/5}  \big) } \\
  &\leq (8Lb)^2 \sqrt{ \frac{s^5}{cn^{4/5}} \log 2n }
\end{align*}
And
\begin{align*}
\sup_{h \in \mathcal{G}}  \Big| \|h\|^2_n - \|h\|^2_P \Big| &\leq 
\sup_{h_\epsilon} \Big| \|h_\epsilon\|^2_n - \|h_\epsilon\|^2_P \Big| 
        + \frac{1}{n^{2/5}} C^2 s^2 (Lb)^3 \\
  &\leq (8Lb)^2 \sqrt{ \frac{s^5}{c n^{4/5}} \log 2 n}
     + (CLb)^2 \sqrt{ \frac{s^4}{n^{4/5}} } \\
  &\leq \mathbf{c} (Lb)^3 \sqrt{ \frac{s^5}{n^{4/5}} \log 2n}
\end{align*}

\rule{5cm}{0.4pt}
\vspace{0.2in}

\textbf{Concavity start}.

We start from the very beginning, where $\hat{g}_k$ is defined as $\min_{g_k \in \mathcal{C}^1_L} \| y - \hat{f} - g_k \|_n^2 + \lambda \| g_k \|_\infty$.

\begin{align*}
\| y - \hat{f} - \hat{g}_k \|_n^2 + \lambda \| \hat{g} \|_\infty &\leq
   \| y - \hat{f} - g^*_k \|_n^2 + \lambda \| g^* \|_\infty \\
\| y - \hat{f} - \hat{g}_k \|_n^2 &\leq \| y - \hat{f} - g^*_k \|_n^2 + \lambda 2 Lb \\
 &\\
\| f_0 - \hat{f} - \hat{g}_k + w\|_n^2 & \leq \| f_0 - \hat{f} - g^*_k + w \|_n^2 
   +\lambda 2 Lb \\
\| f_0 - \hat{f} - \hat{g}_k \|_n^2 - \|f_0 -\hat{f} - g^*_k\|_n^2 &\leq
   2 \langle w, \hat{g}_k - g^*_k \rangle_n + \lambda 2Lb
\end{align*}

Using the chaining result, setting $s=1$, we have, with probability at least $1-\delta$,
\begin{align*}
\| f_0 - \hat{f} - \hat{g}_k \|_n^2 - \|f_0 - \hat{f} - g^*_k \|_n^2 &\leq
  \mathbf{c} (Lb)^2 \sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta} }+ \lambda 2 Lb
\end{align*}

Setting $\delta = 1/n$, using \emph{uniform convergence}, we have
\begin{align*}
\| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \|f_0 - \hat{f} - g^*_k \|_P^2 &\leq
  \mathbf{c} (Lb)^2 \sigma \sqrt{ \frac{1}{n} \log 4n }+ \lambda 2 Lb +
  \mathbf{c} (Lb)^3 \sqrt{\frac{s^5}{n^{4/5}} \log 2n } \\
 &\leq \mathbf{c}(Lb)^3 \sigma \sqrt{\frac{s^5}{n^{4/5}} \log 4n} + \lambda 2 Lb
\end{align*}

\rule{5cm}{0.4pt}
\vspace{0.2in}

Now comes \textbf{concavity removal version 2}.

The goal is to bound radius of approximation between $\| f_0 - \hat{f} - g^*_k \|_P^2$ and $\| f_0 - f^* - g^*_k \|_P^2$ and likewise for $\hat{g}_k$.

\begin{align*}
\| f_0 - \hat{f} - g^*_k \|_P^2 - \| f_0 - f^* - g^*_k\|_P^2 &\leq 
    \| f_0 - \hat{f} \|_P^2 - \|f_0 - f^*\|_P^2 - 2\langle f_0 - \hat{f}, g^*_k \rangle
   + 2 \langle f_0 - f^*, g^*_k \rangle \\
 &\leq \mathbf{c} (Lb)^3 \sqrt{ \frac{s^5}{n^{4/5}} \log 4n} + \lambda 2 sLb + 
    2 | \langle \hat{f} - f^*, g^*_k \rangle |  \\
 &\leq  \mathbf{c} (Lb)^3 \sqrt{ \frac{s^5}{n^{4/5}} \log 4n} + \lambda 2 sLb + 
    2 \| \hat{f} - f^* \|_P \| g^*_k \|_P \\
&\leq  \mathbf{c} (Lb)^3 \sqrt{ \frac{s^5}{n^{4/5}} \log 4n} + \lambda 2 sLb +
   \mathbf{c} 2Lb \sqrt{ (Lb)^3 \sqrt{ \frac{s^5}{n^{4/5}} \log 4n} + \lambda 2sLb} 
\end{align*}

The same bound likewise holds for $\hat{g}_k$.

\rule{5cm}{0.4pt}
\vspace{0.2in}

\newpage
\section{2/15/2014}
